Solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-06-14 paper/paper.tex
Updated figures

\begin{table}
\small
\begin{tabular}{|c|cCc|}
 \hline 
Days & Observed diff & \%  & p-val \\ \hline
-1 0 & -0.64 & 28.00\%\geq 0 & 0.23 \\ 
-1 1 & 0.99 & 22.40\%\leq 0 & 0.86 \\ 
 1 0 & -1.63 & 12.40\%\geq 0 & 0.16 \\ 
\hline
\end{tabular}
\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
\label{BootstrapDifferenceTable}
\end{table}

@@

\begin{figure}[tp!]
	\centering
	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t020-tf25-GOES6.eps}
	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBz-case24-t025-tf30-GOES6.eps}
	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
	\label{fig:RhoBinned}
\end{figure}

>>>>

\begin{table}
\small

\input{../tables/DeltaBootstraps-case10.txt}
\caption{Results of test on of means of $\rho_{eq}$ shown in the top panel of Figure~\ref{DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
\label{BootstrapDifferenceTable}
\end{table}

@@

\begin{figure}[tp!]
	\centering
	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t020-tf25-GOES6.eps}
	\includegraphics[scale=0.40]{figures/RhoBinned/RhoBinnedBzIMF-case24-t025-tf30-GOES6.eps}
	\caption{Binning \req\ events by $B_z$ value (a) at onset and four hours before, and (b) at onset and four hours after.}
	\label{fig:RhoBinned}
\end{figure}
